PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat.raw %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

# Neurological frequencies

```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

@@

>>>>

## COVID positive test (antibody or swab)
```{r create COVID positive test variable}
dat.raw <- dat.raw %>% 
  mutate(covid_test_positive = 
           case_when(
             respiratory.results_antibody_test == "Negative" & 
               respiratory.throat_swab_test_nose == "Negative" ~ 0,
             respiratory.results_antibody_test == "Positive" | 
               respiratory.throat_swab_test_nose == "Positive" ~ 1
           ))

dat.raw %>% 
  count(covid_test_positive)
```

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat.raw %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

#Rough count
dat.raw %>%
  count(covid_probable_case_incl_screening)
```

@@

# Neurological frequencies
** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

@@

**ADD SCORING FOR NEURO MEASURES**
